Concentration of Maxima and Fundamental Limits in High-Dimensional Testing and Inference

### 2020-08-20 preamble.tex
minor edits
added

1) ?.Example.tex files for each chapter conforming to the current style.

2) Began the "index".  If you want to include a term do \index{term}{term}

3) Fixed the level of the table-of-contents.

{\bf Target audience.} The original research presented in this text originates from the doctoral dissertation of the first author in the 
Statistics department at the University of Michigan, Ann Arbor.  The main goal of this text is to provide a comprehensive treatment of the
exact and approximate support recovery problems by utilizing existing and newly developed probabilistic tools on concentration of maxima.
The text also provides a self-contained introduction to the state-of-the-art in the dynamic area of phase-transitions in high-dimensional 
testing and inference.  It is accessible to doctoral students in Statistics with background in measure-theoretic probability and  
statistics as well as to researchers in applied fields working with high-dimensional data sets.  The text can be used as a reference and a
supplement to a special topics course on high-dimensional inference.

>>>>

{\bf Target audience.} The original research presented in this text originates from the doctoral dissertation of the first author in the 
Statistics department at the University of Michigan, Ann Arbor.  The main goal of this text is to provide a comprehensive treatment of the
exact and approximate support recovery problems by utilizing existing and newly developed probabilistic tools on concentration of maxima.
The text also provides a quick introduction to the state-of-the-art in the dynamic area of phase-transitions in high-dimensional 
testing and inference.  It is accessible to doctoral students in Statistics with background in measure-theoretic probability and  
statistics as well as to researchers in applied fields working with high-dimensional data sets.  The text can be used as a reference and a
supplement to a special topics course on high-dimensional inference.
